---
title: "Journal (reproducible report)"
author: "Ole Räthcke"
date: "2020-11-23"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---


# Intro to the tidyverse

```{r}
library(tidyverse)
library(readxl)
bikes_tbl      <- read_excel(path = "00_data/01_bike_sales/01_raw_data/bikes.xlsx")
orderlines_tbl <- read_excel("00_data/01_bike_sales/01_raw_data/orderlines.xlsx")
bikeshops_tbl  <- read_excel("00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")
bike_orderlines_joined_tbl <- orderlines_tbl %>%
  left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))
bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%

  separate(col    = location,
           into   = c("city", "state"),
           sep    = ", ") %>%
  
  
  mutate(total.price = price * quantity) %>%
  
  
  select(-...1, -gender) %>%
  
 
  select(-ends_with(".id")) %>%
  
  
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>% 
  
  
  select(order.id, contains("order"), contains("model"), contains("category"),
         price, quantity, total.price,
         everything()) %>%
  
  
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))

library(lubridate)

sales_by_state_tbl <- bike_orderlines_wrangled_tbl %>%
  
  
  select(state, total_price) %>%
  
  
  group_by(state) %>% 
  summarize(sales = sum(total_price)) %>%
  
  
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))

sales_by_state_tbl %>%
  
  
  ggplot(aes(x = state, y = sales)) +
  
  
  geom_col(fill = "#2DC6D6") + # Use geom_col for a bar plot
  geom_label(aes(label = sales_text)) + # Adding labels to the bars
  geom_smooth(method = "lm", se = FALSE) + # Adding a trendline
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by State",
    x = "", # Override defaults for x and y
    y = "Revenue"
  )

library(lubridate)

sales_by_state_year_tbl <- bike_orderlines_wrangled_tbl %>%
  
  
  select(order_date,state, total_price) %>%
  mutate(year = year(order_date)) %>%
  unite(lols,state,year,sep=", ") %>%
  
  group_by(lols) %>% 
  summarize(sales = sum(total_price)) %>%

  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €")) 
  
a=1:12
plot<-function(x) {
  num = x+4*(x-1)
  num4= num+4
  state_sales_by_year_tbl <- sales_by_state_year_tbl %>%
    filter(row_number()== num:num4) %>%
    separate(col    = lols,
             into   = c("state", "year"),
             sep    = ", ") 
  name<- state_sales_by_year_tbl%>%pull(state)
  state_sales_by_year_tbl%>%
    ggplot(aes(x = year, y = sales)) +
    

    geom_col(fill = "#2DC6D6") + # Use geom_col for a bar plot
    geom_label(aes(label = sales_text)) + # Adding labels to the bars
    geom_smooth(method = "lm", se = FALSE) + # Adding a trendline
    
  
    scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                      decimal.mark = ",", 
                                                      prefix = "", 
                                                      suffix = " €")) +
    labs(
      title    = name[1],
      x = "", # Override defaults for x and y
      y = "Revenue"
    )
  
}
```
## Plots
```{r}
plot(1)
plot(2)
plot(3)
plot(4)
plot(5)
plot(6)
plot(7)
plot(8)
plot(9)
plot(10)
plot(11)
plot(12)
```
<<<<<<< HEAD

# Data Acquisition

```{r}
library(RSQLite)
library(dplyr)
library(httr)
library(tidyverse) 
library(rvest)    
library(xopen)     
library(jsonlite) 
library(glue)     
library(stringi)  

```
## API reading
```{r}
get_pkm_name<-function(ID){
  url<-glue("https://pokeapi.co/api/v2/pokemon/{ID}/")
  pokemon<- url%>%GET()%>%.$content %>% 
    rawToChar() %>% 
    fromJSON()%>% .[11]%>%.[[1]]%>%
    enframe( value = "Name")%>%
    select(Name)
  pokemon
}
pokemon_lst <- map(1:151,get_pkm_name )
pokemon_tbl <- bind_rows(pokemon_lst)
pokemon_tbl

```
## RoseBikeScraping
```{r,eval=FALSE}
url_home          <- "https://www.rosebikes.com"
html_home         <- read_html(url_home)
bike_category_tbl <- html_home %>%
  html_nodes(css = ".main-navigation-category-with-tiles__tile-link")%>%
  html_attr('href') %>%
  enframe(name = "position", value = "subdirectory")%>%
  mutate(
    url = glue("https://www.rosebikes.com{subdirectory}")
  )

bike_url<-function(url){
  html<- read_html(url)
  bike_category_tbl <- html %>%
    html_nodes(css = ".catalog-navigation__link")%>%
    html_attr('href') %>%
    enframe(name = "position", value = "subdirectory")%>%
    mutate(
      url = glue("https://www.rosebikes.com{subdirectory}")
    )
  if(is_empty(bike_category_tbl[[1]])){
    tibble ("url" =url)
  }
  else{
    bike_category_tbl
  }
}

bike_url2<-function(url){
  html<- read_html(url)
  bike_category_tbl <- html %>%
    html_nodes(css = ".catalog-category-bikes__button")%>%
    html_attr('href') %>%
    enframe(name = "position", value = "subdirectory")%>%
    mutate(
      url = glue("https://www.rosebikes.com{subdirectory}")
    )
  if(is_empty(bike_category_tbl[[1]])){
    tibble ("url" =url)
  }
  else{
    bike_category_tbl
  }
}
bike_category_url_vec <- bike_category_tbl %>% 
  pull(url)
bike_url_lst <- map(bike_category_url_vec, bike_url)
bike_url_tbl <- bind_rows(bike_url_lst)

bike_category_url_vec2 <- bike_url_tbl %>% 
  pull(url)
bike_url_lst2 <- map(bike_category_url_vec2, bike_url2)
bike_url_tbl2 <- bind_rows(bike_url_lst2)
#here im cutting of the Kids bikes because of different layout :)
bike_url_tbl2<-bike_url_tbl2%>%filter(row_number()== 1:50) 

bike_price<-function(url){
  html<- read_html(url)
  price <- html %>%
    html_nodes(css = ".catalog-category-model__price-current-value")%>%
    html_text() %>%
    str_remove(pattern = "\n")%>%
    str_remove(pattern = "\200")%>%
    str_remove(pattern = "\n")
  name <- html %>%
    html_nodes(css = ".catalog-category-model__title")%>%
    html_text() %>%
    str_remove(pattern = "\n")%>%
    str_remove(pattern = "\200")%>%
    str_remove(pattern = "\n")
  tibble(
    "price"= price,
    "model"= name,
  )

}

bike_url_vec <- bike_url_tbl2 %>% 
  pull(url)
bike_price_lst <- map(bike_url_vec, bike_price)
bike_price_tbl <- bind_rows(bike_price_lst)
bike_price_tbl


```

# Data Wrangling
```{r,eval=FALSE}
library(readxl)
library(data.table)
library(vroom)

assignee_types <- list(
  id = col_character(),
  type = col_character(),
  name_first = col_skip(),
  name_last = col_skip(),
  organization = col_character()
)

patent_assignee_types <- list(
  patent_id = col_character(),
  assignee_id = col_character(),
  location_id = col_skip()
)
patent_types <- list(
  id = col_character(),
  type = col_skip(),
  number = col_skip(),
  country = col_skip(),
  date = col_date("%Y-%m-%d"),
  abstract = col_skip(),
  title = col_skip(),
  kind = col_skip(),
  num_claims = col_skip(),
  filename = col_skip(),
  withdrawn = col_skip()
)
uspc_types <- list(
  uuid = col_skip(),
  patent_id = col_character(),
  mainclass_id = col_character(),
  subclass_id = col_skip(),
  sequence = col_character()
)
assignee <- vroom(
  file       = "00_data/03_patent/assignee.tsv", 
  delim      = "\t", 
  col_types  = assignee_types,
  na         = c("", "NA", "NULL")
)
patent_assignee <- vroom(
  file       = "00_data/03_patent/patent_assignee.tsv", 
  delim      = "\t", 
  col_types  = patent_assignee_types,
  na         = c("", "NA", "NULL")
)
patent <- vroom(
  file       = "00_data/03_patent/patent.tsv", 
  delim      = "\t", 
  col_types  = patent_types,
  na         = c("", "NA", "NULL")
)
uspc <- vroom(
  file       = "00_data/03_patent/uspc.tsv", 
  delim      = "\t", 
  col_types  = uspc_types,
  na         = c("", "NA", "NULL")
)
setDT(assignee)
setDT(patent_assignee)
setDT(patent)
setkey(assignee,id)
setkey(patent_assignee,assignee_id)
setkey(patent,id)

organization_patent<-assignee[patent_assignee]
organization_sum<-organization_patent%>%
  .[,.N,by=organization]%>%
  .[order(-N)]
#organization_patent2<-patent_assignee[assignee, on = c(assignee_id="id")]
#organization_sum2<-organization_patent2[,sum(.N),by=organization]

setkey(organization_patent,patent_id)
organization_date<-organization_patent[patent]
organization_date<-organization_date%>%
  separate(col  = date,
           into = c("year", "month", "day"),
           sep  = "-", remove = FALSE)
organization_sum2019<-organization_date[year=="2019",sum(.N),by=organization]
Top10_2019<-organization_sum2019%>%.[order(-V1)]%>%.[organization!=is.na(organization)]%>%
  .[1:10]

setDT(uspc)
setkey(uspc,patent_id)
organization_uspc<-organization_patent[uspc]
Top10<-organization_sum%>%.[order(-N)]%>%.[organization!=is.na(organization)]%>%
  .[1:10]
setkey(Top10,organization)
setkey(organization_uspc,organization)
Top10_uspc<-organization_uspc[Top10]
Top10_uspc_sum<-Top10_uspc%>%
  .[sequence==0,.N,by=.(mainclass_id)]%>%
  .[order(-N)]
```
## Question One
```{r}
Top10
```
## Question Two
```{r}
Top10_2019
```
## Question Three
```{r}
Top10_uspc_sum
```




# Data Visualization

```{r}
library(tidyverse)
library(lubridate)
library(scales)
library(ggrepel)
covid_data_tbl <- read_csv("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv")
data_ger<-covid_data_tbl%>%
  filter(countriesAndTerritories=="Germany"|countriesAndTerritories=="United_States_of_America"|countriesAndTerritories=="Spain"|countriesAndTerritories=="France"|countriesAndTerritories=="United_Kingdom")%>%
  mutate(date=dmy(dateRep))%>%
  arrange(date)%>%
  group_by(countriesAndTerritories)%>%
  mutate(cases_sum=cumsum(cases))%>%
  ungroup()

data<-tail(data_ger,1)
data_ger %>%
  
  # Canvas
  ggplot(aes(x = date, y = cases_sum, color = countriesAndTerritories )) +
  
  # Geometries 
  geom_line(size = 1)+
  scale_x_date(labels = date_format("%B"), breaks='1 month')+
  scale_y_continuous(breaks = seq(0, 15000000, by = 2500000),
                     labels = scales::dollar_format(scale = 1/1e6, 
                                                    prefix = "", 
                                                    suffix = "M")) +
  labs(
    title = "COVID-19 confirmed cases worldwide",
    subtitle = "As of 29-11-2020, Europe had more cases than the USA",
    x = "Year 2020",
    y = "Cumulative Cases"
  )+
  scale_color_brewer(palette = "Set1",name="Countries")+
  geom_label_repel(inherit.aes = FALSE, 
                   data = data,
                   aes(x = date, y = cases_sum, label = cases_sum),
                   nudge_x=-40)+
  theme_light() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    title = element_text(face = "bold", color = "#08306B"),
    legend.position="bottom"
    
  )+guides(color=guide_legend(nrow=2,byrow=TRUE))
```

```{r} 
world <- map_data("world")

Deaths_tbl<-covid_data_tbl%>%
  group_by(countriesAndTerritories)%>%
  summarise(total_deaths = sum(deaths/popData2019))%>%
  ungroup()%>% 
  mutate("Mortality Rate"= scales::percent(total_deaths))%>%
  mutate(across(countriesAndTerritories, str_replace_all, "_", " ")) %>%
  mutate(countriesAndTerritories = case_when(
    
    countriesAndTerritories == "United Kingdom" ~ "UK",
    countriesAndTerritories == "United States of America" ~ "USA",
    countriesAndTerritories == "Czechia" ~ "Czech Republic",
    TRUE ~ countriesAndTerritories
    
  ))
plot_data<-left_join(world, Deaths_tbl, by = c("region"="countriesAndTerritories"))

plot_data%>% ggplot( aes(long, lat, group = group,fill = `total_deaths`))+
  geom_map(aes(map_id=region),map = plot_data, color = "darkgrey")+
  
  scale_fill_gradient(low="blue", high="red",
                      name="Mortality Rate",
                      breaks = seq(0, 0.002, by = 0.0002),
                      labels = scales::dollar_format(scale = 1/1e-2,
                                                     prefix = "",
                                                     suffix = "%"))+
  labs(
    title = "Confirmed COVID-19 deaths relative to the size of the population",
    subtitle = "More than 1,2 Million COVID-19 deaths worldwiede",
    x = "",
    y = ""
  )+
  theme_light() +
  theme(
    title = element_text(face = "bold", color = "darkgrey"),
    axis.text.x=element_blank(),
    axis.text.y=element_blank()
    
  )
```
